Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2021-09-27 reports/manuscript.Rmd
Revise workflow and add table

---
title: "Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review"
author:
  - name: Taren Sanders
    url: https://orcid.org/0000-0002-4504-6008
    affiliation: Australian Catholic University
    affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
    orcid_id: 0000-0002-4504-6008
  - name: Philip Parker
    url: https://orcid.org/0000-0002-4604-8566 
    affiliation: Australian Catholic University
    affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
    orcid_id: 0000-0002-4604-8566
  - name: Michael Noetel
    url: https://orcid.org/0000-0002-6563-8203 
    affiliation: Australian Catholic University
    affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
    orcid_id: 0000-0002-6563-8203
  - name: Chris Lonsdale
    url: https://orcid.org/000-0002-2523-5565  
    affiliation: Australian Catholic University
    affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
    orcid_id: 000-0002-2523-5565 
date: "`r Sys.Date()`"
repository_url: https://github.com/Motivation-and-Behaviour/screen_umbrella
bibliography: combined.bib
csl: nature.csl
always_allow_html: true
output:
  github_document:
    html_preview: false
    pandoc_args: "--wrap=none"
---

@@

render_img <- knitr::pandoc_to()=="html5"
inc_ref <- knitr::pandoc_to()!="html5"

# Uncomment to run outside of pipeline
library(tidyverse)
library(targets)
library(xfun)
library(DiagrammeR)
```

```{r, load-targets}
targets::tar_load(c("prisma", "effects_clean", "reviews_table", "plots", 
           "studies_results", "comparison_plots", "combined_effects", 
           "combined_bib"), 
         store = here::here("_targets"))
```

@@

*Statistical Credibility*. We employed a statistical classification approach to grade the statistical credibility of the effect sizes in the literature. To be considered credible an effect needed to be derived from a combined sample of >1,000 and have non-significant tests of publication bias (i.e., Egger’s test and excess significance test).

@@

The searches yielded `r format(prisma$data$value[1], big.mark=",")` results, of which `r format(prisma$data$value[2], big.mark=",")` were removed as duplicates. After screening titles and abstracts, we assessed `r format(prisma$data$value[5], big.mark=",")` full-texts for inclusion. `r str_to_sentence(numbers_to_words(prisma$data$value[8], and=TRUE))` met the inclusion criteria and we extracted the data of these studies. Figure \@ref(fig:prisma) presents the full results of the study selection process.

```{r prisma, eval=render_img, fig.cap="PRISMA Diagram"}
prisma$diag
```

@@

The most frequently reported exposures were `r knitr::combine_words(freq_exposures$out[1:4])`. The most frequently reported outcomes were `r knitr::combine_words(freq_outcomes$out[1:5])`. In most cases (`r paste0(sum(freq_combos$n==1), "/", nrow(effects_clean))`), there was only one exposure/outcome combination, with `r sum(freq_combos$n==2)` appearing twice, and `r sum(freq_combos$n>2)` three or more times. Full characteristics of the included studies are provided in Table X.

```{r quality}
qual_data <- reviews_table$data %>%
  filter(`Outcomes Assessed` !="<ul><li></li></ul>")

reviews_count <- qual_data %>% 
  mutate(across("Eligibility Criteria Predefined And Specified":"Heterogeneity Assessed", as.factor)) %>% 
  rowwise() %>% 
  mutate(count_low = sum(c_across("Eligibility Criteria Predefined And Specified":"Heterogeneity Assessed")=="Low"))

@@

reviews_count <-
  reviews_count %>%
  select("Eligibility Criteria Predefined And Specified":"Heterogeneity Assessed") %>%
  gather(name, value) %>%
  count(name, value) %>%
  arrange(desc(n))

@@

n_low_hetero <-
  reviews_count[reviews_count$name == "Heterogeneity Assessed" &
                  reviews_count$value == "Low", "n"][[1]]
n_low_char <-
  reviews_count[reviews_count$name == "Included Studies Listed With Important Characteristics And Results Of Each" &
                  reviews_count$value == "Low", "n"][[1]]
n_low_search <-
  reviews_count[reviews_count$name == "Literature Search Strategy Comprehensive And Systematic" &
                  reviews_count$value == "Low", "n"][[1]]

n_unclear_elig <-
  reviews_count[reviews_count$name == "Eligibility Criteria Predefined And Specified" &
                  reviews_count$value == "Unclear", "n"][[1]]

n_high_dualscreen <-
  reviews_count[reviews_count$name == "Dual Independent Screening Review" &
                  reviews_count$value == "High", "n"][[1]]
n_unclear_dualscreen <-
  reviews_count[reviews_count$name == "Dual Independent Screening Review" &
                  reviews_count$value == "Unclear", "n"][[1]]

n_high_dualquality <-
  reviews_count[reviews_count$name == "Dual Independent Quality Assessment" &
                  reviews_count$value == "High", "n"][[1]]
n_unclear_dualquality <-
  reviews_count[reviews_count$name == "Dual Independent Quality Assessment" &
                  reviews_count$value == "Unclear", "n"][[1]]

@@

The quality of the included studies was mixed. Most studies assessed heterogeneity `r qual_str(n_low_hetero, nrow(qual_data), " low ", suffix=" of studies)")`, reported the characteristics of the included studies `r qual_str(n_low_char, nrow(qual_data), " low ")`, and used a comprehensive and systematic search strategy `r qual_str(n_low_search, nrow(qual_data), " low ")`. Most studies did not clearly report if their eligibility criteria was predefined `r qual_str(n_unclear_elig, nrow(qual_data), " unclear ")`. A similar trend was observed for dual independent quality assessment `r dualqualstr`. Overall, only `r all_low` were graded as *low* risk of bias on all criteria.

@@

```{r eduplot, eval=render_img, fig.width=plots[[1]]$dims[[1]], fig.height=plots[[1]]$dims[[2]], fig.cap="Education outcomes"}
plots[[1]]$plot
```

@@

```{r healthplot, eval=render_img, fig.width=plots[[2]]$dims[[1]], fig.height=plots[[2]]$dims[[2]], fig.cap="Health and health-related behaviour outcomes"}
plots[[2]]$plot
```

@@

```{r refs, eval=inc_ref, results='asis'}
"# References"
```

>>>>

---
title: "Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review"
author:
  - name: Taren Sanders
    affiliation: Institute for Positive Psychology and Education, Australian Catholic
      University
    affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
    orcid_id: 0000-0002-4504-6008
  - name: Philip Parker
    affiliation: Institute for Positive Psychology and Education, Australian Catholic
      University
    affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
    orcid_id: 0000-0002-4604-8566
  - name: Michael Noetel
    affiliation: School of Health and Behavioural Sciences, Australian Catholic University
    affiliation_url: https://www.acu.edu.au/about-acu/faculties-directorates-and-staff/faculty-of-health-sciences/school-of-behavioural-and-health-sciences
    orcid_id: 0000-0002-6563-8203
  - name: Chris Lonsdale
date: '`r format(Sys.Date())`'
repository_url: https://github.com/Motivation-and-Behaviour/screen_umbrella
bibliography: combined.bib
csl: nature.csl
params:
  render_img: true
  inc_ref: false
---

@@

# Uncomment to run outside of pipeline
# library(tidyverse)
# library(targets)
# library(xfun)
```

```{r, load-targets}
targets::tar_load(c("prisma", "effects_clean", "reviews_tables", "tables_df",
                    "plots", "studies_results", "comparison_plots", 
                    "combined_effects", "combined_bib"), 
         store = here::here("_targets"))
```

@@

*Statistical Credibility*. We employed a statistical classification approach to grade the statistical credibility of the effect sizes in the literature. To be considered credible an effect needed to be derived from a combined sample of >1,000 and have non-significant tests of publication bias (i.e., Egger’s test and excess significance test). We performed these analyses, and tehrefore the review needed to provide usable study-level data in order to be included.

@@

The searches yielded `r format(prisma$data$value[1], big.mark=",")` results, of which `r format(prisma$data$value[2], big.mark=",")` were duplicates. After screening titles and abstracts, we assessed `r format(prisma$data$value[5], big.mark=",")` full-texts for inclusion. `r str_to_sentence(numbers_to_words(prisma$data$value[8], and=TRUE))` met the inclusion criteria and we extracted the data of these meta-analyses. Figure \@ref(fig:prisma) presents the full results of the selection process.

```{r prisma, fig.cap="PRISMA Diagram"}
prisma$diag
```

@@

The most frequently reported exposures were `r knitr::combine_words(freq_exposures$out[1:4])`. The most frequently reported outcomes were `r knitr::combine_words(freq_outcomes$out[1:5])`. In most cases (`r paste0(sum(freq_combos$n==1), "/", nrow(effects_clean))`), there was only one exposure/outcome combination, with `r sum(freq_combos$n==2)` appearing twice, and `r sum(freq_combos$n>2)` three or more times. Full characteristics of the included studies are provided in Table \@ref(tab:desctable).

```{r desctable, layout="l-screen-inset shaded"}
reviews_tables[[1]]$table
```

```{r quality}
qual_data <- 
  tables_df %>%
  filter(table=="main") %>% 
  distinct(covidence_id, .keep_all = TRUE) %>% 
  select(eligibility_criteria_predefined_and_specified:heterogeneity_assessed)

reviews_count <- qual_data %>%
  mutate(
    across(
      eligibility_criteria_predefined_and_specified:heterogeneity_assessed,
      as.factor
    )
  ) %>%
  rowwise() %>%
  mutate(count_low = sum(
    c_across(
      eligibility_criteria_predefined_and_specified:heterogeneity_assessed
    ) == "low"
  ))

@@

reviews_count <-
  reviews_count %>%
  select(eligibility_criteria_predefined_and_specified:heterogeneity_assessed) %>%
  gather(name, value) %>%
  count(name, value) %>%
  arrange(desc(n))

@@

n_low_hetero <-
  reviews_count[reviews_count$name == "heterogeneity_assessed" &
                  reviews_count$value == "low", "n"][[1]]
n_low_char <-
  reviews_count[reviews_count$name == "included_studies_listed_with_important_characteristics_and_results_of_each" &
                  reviews_count$value == "low", "n"][[1]]
n_low_search <-
  reviews_count[reviews_count$name == "literature_search_strategy_comprehensive_and_systematic" &
                  reviews_count$value == "low", "n"][[1]]

n_unclear_elig <-
  reviews_count[reviews_count$name == "eligibility_criteria_predefined_and_specified" &
                  reviews_count$value == "unclear", "n"][[1]]

n_high_dualscreen <-
  reviews_count[reviews_count$name == "dual_independent_screening_review" &
                  reviews_count$value == "high", "n"][[1]]
n_unclear_dualscreen <-
  reviews_count[reviews_count$name == "dual_independent_screening_review" &
                  reviews_count$value == "unclear", "n"][[1]]

n_high_dualquality <-
  reviews_count[reviews_count$name == "dual_independent_quality_assessment" &
                  reviews_count$value == "high", "n"][[1]]
n_unclear_dualquality <-
  reviews_count[reviews_count$name == "dual_independent_quality_assessment" &
                  reviews_count$value == "unclear", "n"][[1]]

@@

The quality of the included meta-analyses was mixed. Most assessed heterogeneity `r qual_str(n_low_hetero, nrow(qual_data), " low ", suffix=" of studies)")`, reported the characteristics of the included studies `r qual_str(n_low_char, nrow(qual_data), " low ")`, and used a comprehensive and systematic search strategy `r qual_str(n_low_search, nrow(qual_data), " low ")`. Most reviews did not clearly report if their eligibility criteria was predefined `r qual_str(n_unclear_elig, nrow(qual_data), " unclear ")`. Many reviews also did not complete dual independent screening of abstracts and full text `r qual_str(n_high_dualscreen, nrow(qual_data), " high ")` or did not clearly report the method of screening `r qual_str(n_unclear_dualscreen, nrow(qual_data), " unclear ")`. Many reviews  also did not complete A similar trend was observed for dual independent quality assessment `r dualqualstr`. Overall, only `r all_low` meta-analyses were graded as *low* risk of bias on all criteria.

@@

```{r eduplot, fig.width=plots[[1]]$dims[[1]], fig.height=plots[[1]]$dims[[2]], fig.cap="Education outcomes"}
plots[[1]]$plot
```

@@

```{r healthplot, fig.width=plots[[2]]$dims[[1]], fig.height=plots[[2]]$dims[[2]], fig.cap="Health and health-related behaviour outcomes"}
plots[[2]]$plot
```

@@

```{r refs, results='asis'}
if (params$inc_ref) "# References"
```
